Faithful Model Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2024-01-10 paper/camera-ready/altmeyer.tex
some touches added

% Numbered Environments:
\newtheorem{definition}{Definition}[section]
\newtheorem{question}{Research Question}[section]

\setcounter{secnumdepth}{1} %May be changed to 1 or 2 if section numbers are desired.

@@

\title{Faithful Model Explanations through\\
Energy-Constrained Conformal Counterfactuals}
\author{
    %Authors
    % All authors must be in the same font size and format.
    Patrick Altmeyer\textsuperscript{\rm 1},
    Mojtaba Farmanbar\textsuperscript{\rm 2},
    Arie van Deursen\textsuperscript{\rm 1},
    Cynthia C. S. Liem\textsuperscript{\rm 1}
}
\affiliations{
    %Afiliations
    \textsuperscript{\rm 1}Delft University of Technology,\\
    Faculty of Electrical Engineering, Mathematics and Computer Science\\
    \textsuperscript{\rm 2}ING Bank\\
    p.altmeyer@tudelft.nl
%
% See more examples next
}

@@

\section{Why Fidelity is not Enough: A Motivational Example}\label{fidelity}

@@

\section{Faithful first, Plausible second}\label{faithfulness}

@@

\subsection{Quantifying the Model's Generative Property}

>>>>

% Numbered Environments:
\newtheorem{definition}{Definition}[section]
\renewcommand{\thedefinition}{\arabic{definition}}
\newtheorem{question}{Research Question}[section]
\renewcommand{\thequestion}{\arabic{question}}

% \setcounter{secnumdepth}{1} %May be changed to 1 or 2 if section numbers are desired.

@@

\title{Faithful Model Explanations through\\
Energy-Constrained Conformal Counterfactuals}
\author{
    %Authors
    % All authors must be in the same font size and format.
    Patrick Altmeyer\textsuperscript{\rm 1},
    Mojtaba Farmanbar\textsuperscript{\rm 2},
    Arie van Deursen\textsuperscript{\rm 1},
    Cynthia C. S. Liem\textsuperscript{\rm 1}
}
\affiliations{
    %Afiliations
    \textsuperscript{\rm 1}Delft University of Technology,
    Faculty of Electrical Engineering, Mathematics and Computer Science\\
    \textsuperscript{\rm 2}ING Bank\\
    p.altmeyer@tudelft.nl
%
% See more examples next
}

@@

\section{Why Fidelity Is Not Enough: A Motivational Example}\label{fidelity}

@@

\section{Faithful First, Plausible Second}\label{faithfulness}

@@

\subsection{Quantifying the Model’s Generative Property}
